### 2021-03-29 notes/notes.tex
Take home

@@

>>>>

% Model and task parameter macros
\input{parameters}

@@

\section{Parametrization of the task and the model}
Some of the parameters of the model can be fixed by the physics and scales of
the simulated experiment.

Henceforth, distances are measured in meters and time in seconds. As a
consequence, forces should be measured in Newtons, but bare in mind that what
the model calls ``force'' is no such thing. Instead, ``forces'' in the model
are the distance (in meters) that the real force (in Newtons) would make the
arm move in some $\Delta t$, assuming a mass of 1Kg and zero initial
velocity. This simplification of the terms might come back to bite us in the
ass and might be replaced later. But first, let us speak of real forces.

The force exerted by the mechanical arm depends on the context. In the baseline
context, the force is 0N. Taking inspiration from \todo{Citation needed}, we
take the forces of the other two contexts to be \force and -\force,
respectively. We will assume that $\Delta t = \dt$ \todo{Need to find a good
  way of fixing this}, which represents reaction, processing and decision
times.

Back to the lazy encoding of forces in the model, one can calculate the effects
of these forces on the arm. With a force of 10N and a $\Delta t$ of 50ms, the
total distance the arm will be moved by the force (again, assuming mass of 1Kg)
is given by:
\begin{align}
  d_\plusminus &= \plusminus \frac{1}{2}(\force / 1Kg)((\dt)^2)\\
               &= \plusminus 0.0125m
\end{align}
The agent will try to estimate $d_\plusminus$ during the experiment.

We will assume \todo{This is arbitrary. Might want to justify it later.} that
the participant observes the position of her own hand (visual + proprioceptive)
with Gaussian observation noise with $\mu = 0m$ and $\sigma = 0.005m$.
